---
title: "Smouldering fire in upland swamp soils"
output:
  html_document:
    df_print: paged
---

## Smouldering fire

```{r message=FALSE, warning=FALSE}
library(ggplot2)
library(dplyr)
library(DHARMa)
library(emmeans)
library(parameters)
library(table1)
library(MuMIn)
```


Load data

```{r}
datadir <- "../data"
locations<- read.csv(file.path(datadir, "Sod_locations.csv"))
smouldering <-read.csv(file.path(datadir, "TM5_Complete_Sod_Data_main.csv"))

```


Clean data and tabulate

```{r}
som_gravmoist <- smouldering %>% 
  filter(!Sample=='MH CH 19') %>% 
  left_join(locations) %>% 
  mutate(swamp = substr(Sample,1, 3),
         veg = trimws(substr(Sample,4, 6)),
         bd_mg_per_cm3 = bd_g_per_cm3*1000, #mg
         bd_mg_cat = cut(bd_mg_per_cm3, breaks = c(0,250, 400, 2000)),
         bd_mg_cat = factor(bd_mg_cat, labels = c(200,300,500))) %>% 
    dplyr::select(binomial_burn_status, grav_moist_percent , som_percent, bd_mg_per_cm3, swamp, veg, lat, long, bd_mg_cat) 

table1(~grav_moist_percent + som_percent+ bd_mg_per_cm3 |binomial_burn_status, data = som_gravmoist)
```


### Explore

Plot against burning status.

```{r}
ggplot(som_gravmoist, aes(bd_mg_per_cm3, binomial_burn_status))+
  geom_point()

ggplot(som_gravmoist, aes(grav_moist_percent, binomial_burn_status))+
  geom_point()

ggplot(som_gravmoist, aes(som_percent, binomial_burn_status))+
  geom_point()
```
We expect grav_moist_percent will be strongest predictor.

### Variable selection, forward stepwise

We do this manually  rather than using `stepAIC` as we were getting warnings and wanted to know where they were coming from. We changed from used `AIC` to `AICc` due to reviewer comments, it made no difference to the model chosen.

```{r}
cor(som_gravmoist[,c(2,3,4)])
```
The largest correlation is 0.73 so we aren't worried about multicollinearity.

Models with one predictor:

```{r}
base_mod_smould <- glm(binomial_burn_status ~1, family=binomial, data = som_gravmoist)
base_mod_smould_grav <- glm(binomial_burn_status ~  + grav_moist_percent, family=binomial, data = som_gravmoist)
base_mod_smould_som <- glm(binomial_burn_status ~  +som_percent, family=binomial, data = som_gravmoist)
base_mod_smould_bd <- glm(binomial_burn_status ~  + bd_mg_per_cm3, family=binomial, data = som_gravmoist)

AICc(base_mod_smould, base_mod_smould_grav, base_mod_smould_som, base_mod_smould_bd)
```

grav_moist_percent is best of these models. We keep adding variables

```{r}
base_mod_smould_grav_som <- glm(binomial_burn_status ~  grav_moist_percent + som_percent, family=binomial, data = som_gravmoist)
base_mod_smould_grav_bd <- glm(binomial_burn_status ~  grav_moist_percent + bd_mg_per_cm3, family=binomial, data = som_gravmoist)

AICc(base_mod_smould_grav, base_mod_smould_grav_som, base_mod_smould_grav_bd)
```

Lowest AIC includes grav and bd, so we keep going to see if som improves model. 

```{r}
base_mod_smould_grav_bd_som <- glm(binomial_burn_status ~  grav_moist_percent  +bd_mg_per_cm3+som_percent, family=binomial, data = som_gravmoist)
AICc(base_mod_smould_grav_bd, base_mod_smould_grav_bd_som)

```

Lowest AIC is grav and bd only. 


Check assumptions
```{r}
sim= simulateResiduals(base_mod_smould_grav_bd)
resid = residuals(sim, quantileFunction = qnorm, outlierValues = c(-7,7))
plot(resid~fitted(base_mod_smould_grav_bd))

```
Residuals are okay. 


The model has warnings about 'fitted probabilities numerically 0 or 1 occurred', this is often perfect separation. We look at standard errors of coefficients. 

```{r}
summary(base_mod_smould_grav_bd_som)
```
Standard errors are reasonable. For large values of grav, the probability of burning is appropriately very near 0 (see plots below), so we don't believe there is perfect separation. 


### Inference

Calculate odds ratios. 

```{r message=FALSE, warning=FALSE}
parameters(base_mod_smould_grav_bd, exponentiate = T, ci_method  = "profile", digits = 4)
```

Calculate predictions

```{r}
ems_full_smould = emmip(base_mod_smould_grav_bd, ~ grav_moist_percent +  bd_mg_per_cm3, type = "response",  CIs = TRUE,
      at = list(grav_moist_percent = seq(0,500,by=5),
                bd_mg_per_cm3 = c(200, 300, 500)), plotit = FALSE)

ems_full_smould$bd_mg_cat <- ems_full_smould$bd_mg_per_cm3

ems_full_smould$bd_mg_per_cm3 = factor(ems_full_smould$bd_mg_per_cm3)
write.csv(ems_full_smould,file="../results/pred_smould.csv")

ems_full_smould %>% 
  filter(grav_moist_percent %in% c(50, 100, 150)) %>% 
  transmute(grav_moist_percent, 
            bd_mg_per_cm3,
            pred_burn_prob = round(yvar, 4),
            LCL = round(LCL, 4),
            UCL = round(UCL,4)) 
  
```

Plot.

```{r}
#modify facet labels
bd_names <- as_labeller(
  c('200' = "(a) 200 mg/cm3", '300' = "(b) 300 mg/cm3", '500' = "(c) 500 mg/cm3"))


smould_plot <- ggplot(ems_full_smould, aes(grav_moist_percent, yvar)) +
  geom_ribbon(aes(ymin = LCL, ymax = UCL), alpha = 0.5, fill = "lightgrey")+
  geom_line()+
  geom_point(colour = "grey25", data = som_gravmoist, aes(grav_moist_percent,binomial_burn_status)) +
  xlab("Gravimetric water content (%)")+
  ylab(expression(atop(paste("Probability of smouldering fire"), paste("in swamp substrate (+/-95% CI)"))))+
  theme(axis.text = element_text(size = 12))+
  theme(axis.title = element_text(size = 14), strip.background = element_rect(colour="white", fill="white"))+
  theme(plot.title = element_text(size = 14))+
  theme(strip.text = element_text(size = 14))+
  theme(legend.text = element_text(size = 12))+
  xlim(0,600)+
  facet_grid(~bd_mg_cat, labeller = bd_names)+
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))
smould_plot
ggsave(plot = smould_plot, file = "../results/smould_plot.tiff" , width = 180, height = 100, units = "mm", device = "tiff")
```
Note : The plots contain data from 0-250, 250-400, 400-max but predictions at 200, 300 and 500


