---
title: "Smouldering and flaming fire in upland swamp soils"
output:
  html_document:
    df_print: paged
---

```{r message=FALSE, warning=FALSE}
library(ggplot2)
library(dplyr)
library(DHARMa)
library(emmeans)
library(parameters)
library(table1)
library(MuMIn)
```

### Data

```{r}
datadir <- "../data"
flaming <- read.csv(file.path(datadir,"Sod_Data_flaming_moist_som_main.csv"))

```

There are two burning temperatures, High (BAL40) and Low (BBALFZ). Clean data.

```{r}

burn_data <- flaming %>% 
  filter(!Sample=='MH CH 19') %>% # remove outlier
  mutate(binomial_burn_status = binomial_iCone_burn_status,
         grav_moist_percent = grav_moist_percent_dec2023,
         som_percent = som_percent_Jan24,
         bd_mg_per_cm3 = bd_g_per_cm3_May23,
         Fire_treat = factor(Fire_treat, levels = c("Low", "High"))) 

table1(~grav_moist_percent+bd_mg_per_cm3+som_percent|Fire_treat+binomial_burn_status,data=burn_data)
```




## Flaming fire analysis - BAL40

```{r}
som_gravmoist <- burn_data %>% 
  filter(Fire_treat == "Low")
```



### Explore

Plot against burning status.

```{r}
ggplot(som_gravmoist, aes(bd_mg_per_cm3, binomial_burn_status))+
  geom_point()

ggplot(som_gravmoist, aes(grav_moist_percent, binomial_burn_status))+
  geom_point()

ggplot(som_gravmoist, aes(som_percent, binomial_burn_status))+
  geom_point()
```

We expect grav_moist_percent will be strongest predictor.

### Model

Due to small sample size, we will include only one variable in model to predict burning. Use AICc to choose variable. 

```{r}
base_mod_smould <- glm(binomial_burn_status ~1, family=binomial, data = som_gravmoist)
base_mod_smould_grav <- glm(binomial_burn_status ~  + grav_moist_percent, family=binomial, data = som_gravmoist)
base_mod_smould_som <- glm(binomial_burn_status ~  +som_percent, family=binomial, data = som_gravmoist)
base_mod_smould_bd <- glm(binomial_burn_status ~  + bd_mg_per_cm3, family=binomial, data = som_gravmoist)

AICc(base_mod_smould, base_mod_smould_grav, base_mod_smould_som, base_mod_smould_bd)
```

grav is by far the best predictor


```{r}
BAL40_mod <- base_mod_smould_grav
```


Check assumptions
```{r}
sim= simulateResiduals(BAL40_mod)
resid = residuals(sim, quantileFunction = qnorm, outlierValues = c(-7,7))
plot(resid~fitted(BAL40_mod))

```

Residuals are okay. 

The model has warnings about 'fitted probabilities numerically 0 or 1 occurred', this is often perfect separation. We look at standard errors of coefficients. 

```{r}
summary(BAL40_mod)
```
Standard errors are reasonable. For large values of grav, the probability of burning is appropriately very near 0 (see plots below), so we don't believe there is perfect separation. 



### Inference

Calculate odds ratios. 

```{r message=FALSE, warning=FALSE}
parameters(BAL40_mod, exponentiate = T, ci_method  = "profile", digits = 4)
```

Calculate predictions

```{r}
ems_BAL40 = emmip(BAL40_mod, ~ grav_moist_percent, type = "response",  CIs = TRUE,
      at = list(grav_moist_percent = seq(0,500,by=5)), plotit = FALSE)

write.csv(ems_BAL40,file="../results/prob_BAL40.csv")

ems_BAL40 %>% 
  filter(grav_moist_percent %in% c(50, 100, 150)) %>% 
  transmute(grav_moist_percent, 
            pred_burn_prob = round(yvar, 4),
            LCL = round(LCL, 4),
            UCL = round(UCL,4)) 
  
```

Plot.

```{r message=FALSE, warning=FALSE}

BAL40_plot <- ggplot(ems_BAL40, aes(grav_moist_percent, yvar)) +
  geom_ribbon(aes(ymin = LCL, ymax = UCL), alpha = 0.5, fill = "lightgrey")+
  geom_line()+
  geom_point(colour = "grey25", data = som_gravmoist, aes(grav_moist_percent,binomial_burn_status)) +
  xlab("Gravimetric water content (%)")+
  ylab(expression(atop(paste("Probability of smouldering fire"), paste("in swamp substrate (+/-95% CI)"))))+
  theme(axis.text = element_text(size = 12))+
  theme(axis.title = element_text(size = 14), strip.background = element_rect(colour="white", fill="white"))+
  theme(plot.title = element_text(size = 14))+
  theme(strip.text = element_text(size = 14))+
  theme(legend.text = element_text(size = 12))+
  xlim(0,600)+
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))
BAL40_plot

ggsave(plot = BAL40_plot, file = "../results/BAL40_plot.tiff" , width = 180, height = 150, units = "mm", device = "tiff")
```
## Flaming fire analysis - BALFZ


```{r}
som_gravmoist <- burn_data %>% 
  filter(Fire_treat == "High")
```



### Explore

Plot against burning status.

```{r}
ggplot(som_gravmoist, aes(bd_mg_per_cm3, binomial_burn_status))+
  geom_point()

ggplot(som_gravmoist, aes(grav_moist_percent, binomial_burn_status))+
  geom_point()

ggplot(som_gravmoist, aes(som_percent, binomial_burn_status))+
  geom_point()
```

We expect grav_moist_percent will be strongest predictor.

### Model

Due to small sample size, we will include only one variable in model to predict burning. Use AICc to choose variable. 

```{r}
base_mod_smould <- glm(binomial_burn_status ~1, family=binomial, data = som_gravmoist)
base_mod_smould_grav <- glm(binomial_burn_status ~  + grav_moist_percent, family=binomial, data = som_gravmoist)
base_mod_smould_som <- glm(binomial_burn_status ~  +som_percent, family=binomial, data = som_gravmoist)
base_mod_smould_bd <- glm(binomial_burn_status ~  + bd_mg_per_cm3, family=binomial, data = som_gravmoist)

AICc(base_mod_smould, base_mod_smould_grav, base_mod_smould_som, base_mod_smould_bd)
```

grav is by far the best predictor

```{r}
BALFZ_mod <- base_mod_smould_grav
```


Check assumptions
```{r}
sim= simulateResiduals(BALFZ_mod)
resid = residuals(sim, quantileFunction = qnorm, outlierValues = c(-7,7))
plot(resid~fitted(BALFZ_mod))
```

Residuals are okay. 

### Inference

Calculate odds ratios. 

```{r message=FALSE, warning=FALSE}
parameters(BALFZ_mod, exponentiate = T, ci_method  = "profile", digits = 4)
```

Calculate predictions

```{r}
ems_BALFZ = emmip(BALFZ_mod, ~ grav_moist_percent, type = "response",  CIs = TRUE,
      at = list(grav_moist_percent = seq(0,500,by=5)), plotit = FALSE)

write.csv(ems_BALFZ,file="../results/prob_BALFZ.csv")

ems_BALFZ %>% 
  filter(grav_moist_percent %in% c(50, 100, 150)) %>% 
  transmute(grav_moist_percent, 
            pred_burn_prob = round(yvar, 4),
            LCL = round(LCL, 4),
            UCL = round(UCL,4)) 
  
```

```{r}


BALFZ_plot <- ggplot(ems_BALFZ, aes(grav_moist_percent, yvar)) +
  geom_ribbon(aes(ymin = LCL, ymax = UCL), alpha = 0.5, fill = "lightgrey")+
  geom_line()+
  geom_point(colour = "grey25", data = som_gravmoist, aes(grav_moist_percent,binomial_burn_status)) +
  xlab("Gravimetric water content (%)")+
  ylab(expression(atop(paste("Probability of smouldering fire"), paste("in swamp substrate (+/-95% CI)"))))+
  theme(axis.text = element_text(size = 12))+
  theme(axis.title = element_text(size = 14), strip.background = element_rect(colour="white", fill="white"))+
  theme(plot.title = element_text(size = 14))+
  theme(strip.text = element_text(size = 14))+
  theme(legend.text = element_text(size = 12))+
  xlim(0,600)+
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))
BALFZ_plot
ggsave(plot = BALFZ_plot, file = "../results/BALFZ_plot.tiff" , width = 180, height = 150, units = "mm", device = "tiff")
```

## Combined fire analysis - BALFZ

Does temperature affect probability of burning?


### Model

Fit model and check assumptions

```{r}
flaming_mod <- glm(binomial_burn_status ~ grav_moist_percent + som_percent + bd_mg_per_cm3 + Fire_treat, family=binomial, data = burn_data)
sim= simulateResiduals(flaming_mod)
resid = residuals(sim, quantileFunction = qnorm, outlierValues = c(-7,7))
plot(resid~fitted(flaming_mod))
```

Residuals are okay. 


The model has warnings about 'fitted probabilities numerically 0 or 1 occurred', this is often perfect separation. We look at standard errors of coefficients. 

```{r}
summary(flaming_mod)
```
Standard errors are reasonable. For large values of grav, the probability of burning is appropriately very near 0 (see plots below), so we don't believe there is perfect separation. 

## Inference

Likelihood ratio test

```{r warning=FALSE}
flaming_mod0 <- glm(binomial_burn_status ~ grav_moist_percent + som_percent + bd_mg_per_cm3  , family=binomial, data = burn_data)
anova(flaming_mod0, flaming_mod, test = "LRT")

```

Calculate odds ratios with profile confidence intervals. 

```{r message=FALSE, warning=FALSE}
parameters(flaming_mod, exponentiate = T, ci_method  = "profile", digits = 4)
```


Calculate predictions

```{r}
ems_flaming_comb = emmip(flaming_mod, ~ grav_moist_percent + Fire_treat, type = "response",  CIs = TRUE,
      at = list(grav_moist_percent = seq(0,500,by=5)), plotit = FALSE)

write.csv(ems_flaming_comb,file="../results/pred_flaming_comb.csv")

ems_flaming_comb %>% 
  filter(grav_moist_percent %in% c(50, 100, 150)) %>% 
  transmute(Fire_treat,
            grav_moist_percent, 
            pred_burn_prob = round(yvar, 4),
            LCL = round(LCL, 4),
            UCL = round(UCL,4)) 
  
```





```{r}

BAL40andFZ_plot <- ggplot(ems_flaming_comb, aes(grav_moist_percent, yvar, color= Fire_treat, fill = Fire_treat)) +
  geom_ribbon(aes(ymin = LCL, ymax = UCL), alpha = 0.2, linetype="dashed")+ #fill = "darkgoldenrod3"
  geom_line()+
  geom_point( data = burn_data, aes(grav_moist_percent,binomial_burn_status)) + #colour = "grey25",
  xlab("Gravimetric water content (%)")+
  ylab(expression(atop(paste("Probability of flaming fire in swamp substrate"), paste("(+/-95% CI)"))))+
  #geom_vline(xintercept = 50)+ #tells us what the value and CI are when grav moist is 50%
  scale_fill_manual(values = c("darkgrey", "lightgrey"),labels=c("High intensity fire (BALFZ)", "Lower intensity fire (BAL40)"))+
  theme(legend.position = c(.7,.7))+
  scale_colour_manual(values = c("darkgrey", "lightgrey"), guide="none")+
  guides(fill = guide_legend(override.aes = list(colour = c("darkgrey", "lightgrey"))))+
  theme(axis.text = element_text(size = 12))+
  theme(axis.title = element_text(size = 14))+
  theme(plot.title = element_text(size = 14))+
  theme(strip.text = element_text(size = 14))+
  theme(legend.text = element_text(size = 12))+
  scale_x_continuous(breaks = seq(0, 900, by = 100))+
  theme(legend.title = element_blank())+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))
BAL40andFZ_plot
 ggsave(plot = BAL40andFZ_plot, file = "../results/BAL40andFZ_plot2.tiff" , width = 180, height = 150, units = "mm", device = "tiff")
  #geom_vline(xintercept = 10)#tells us what the value and CI are when grav moist is 10%
```

```{r}


BAL40andFZ_plot_updated <- ggplot(ems_flaming_comb, aes(grav_moist_percent, yvar, color= Fire_treat, fill = Fire_treat)) +
  geom_ribbon(aes(ymin = LCL, ymax = UCL), alpha = 0.2, linetype="dashed")+ #fill = "darkgoldenrod3"
  geom_line()+
  geom_point( data = burn_data, aes(grav_moist_percent,binomial_burn_status)) + #colour = "grey25",
  xlab("Gravimetric water content (%)")+
  ylab(expression(atop(paste("Probability of flaming fire in swamp substrate"), paste("(+/-95% CI)"))))+
  #geom_vline(xintercept = 50)+ #tells us what the value and CI are when grav moist is 50%
  scale_fill_manual(values = c("coral4", "brown1"),labels=c("Wildfire intensity (BALFZ)", "Moderate-intensity (BAL40)"))+
  theme(legend.position = c(.7,.7))+
  scale_colour_manual(values = c("coral4", "brown1"), guide="none")+
  guides(fill = guide_legend(override.aes = list(colour = c("coral4", "brown1"))))+
  theme(axis.text = element_text(size = 12))+
  theme(axis.title = element_text(size = 14))+
  theme(plot.title = element_text(size = 14))+
  theme(strip.text = element_text(size = 14))+
  theme(legend.text = element_text(size = 12))+
  scale_x_continuous(breaks = seq(0, 900, by = 100))+
  theme(legend.title = element_blank())+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))
BAL40andFZ_plot_updated
 ggsave(plot = BAL40andFZ_plot_updated, file = "../results/BAL40andFZ_plot3.tiff" , width = 180, height = 150, units = "mm", device = "tiff")
  #geom_vline(xintercept = 10)#tells us what the value and CI are when grav moist is 10%
```

